Verification of concurrent design patterns with data

### 2019-02-13 2018-Arch-pNets/arch-pNets.tex
Related works: pycots and key-abs

theorem proving? (too much manual effort) we need an example, we could cite Coqcots and Pycots for reconfiguration == LUDO

@@

KeY? (I would call this symbolic execution and assume-guarantee) == LUDO

>>>>

As compositional proof of safety is difficult, some approaches rely on theorem proving to ensure the safety of component operations. Coqots and Pycots\cite{BCDLM:CBSE2014} even allow to prove the safety of reconfiguration procedures which are known to be highly difficult to verify, and massively parametrised. unfortunately the approach relies on a high expertise and significant efforts from the component user as (s)he must prove manually the safety of the reconfiguration process. In this paper, we rely on automatic encoding into a SMT solver making the proof of properties much more automatic, but we cannot prove the safety of the reconfiguration procedure.

@@

In~\cite{DDJO:JLAMP2012}, the authors propose a compositional proof system for distributed objects that is suitable for implementation within the KeY framework~\cite{BHS:Key2007} and uses a Hoare logic approach.
The approach relies on history invariant for each object, separating local reasoning for proving object invariant from global reasoning that relies on well-formedness of traces. Compared to this  approach, we do not  deal with complex history-based specifications because we use interaction specification and SMT-reasoning instead of Hoare logic. Also the correctness of the composition is given by the properties of architectures which allows for more flexibility than well-formedness of traces.
